---
title: "Neighborhood Racial Composition, Built Environment and Health Outcomes (Table 2)"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(nnet)
library(tidyr)
library(tidyverse)
library(dplyr)
library(car)
library(stargazer)
library(reshape)
library(modelsummary)
library(knitr)
library(stringr)
library(effects)

library(lme4)
library(lmerTest)
library(merTools)
library(bife)
library(lfe)
library(texreg)

library(sjPlot) # table functions
library(sjmisc) # sample data

options(scipen = 999)

knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_knit$set(root.dir ='/Users/ahyoungcho/Dropbox/CAR/2022 Summer/')

# Load data 
# df <- readRDS(file = "/Users/ahyoungcho/Dropbox/CAR/2022 Summer/Replication/FinalData/finaldata.rds")
df <- readRDS(file = "../FinalData/finaldata.rds")
```

### Table 2 

#### Neighborhood Composition 

1. Predominantly white: Tracts where there are at least 60% of non-Hispanic whites and no minority group represents more than 20%.
2. Predominantly black: Tracts that have at least 50% non-Hispanic blacks and no more than 20% of another racial/ethnic group
3. Predominantly non-black minority: Tracts consist of at least 50% of a certain non-black minority and no more than 20% of non-Hispanic blacks
Mixed: Tracts that annot be classified into any of the typologies above. 

```{r, message=FALSE, warning=FALSE, include=FALSE}
df_composition <- df %>%
  dplyr::select(-geometry) %>%
  mutate(Composition = ifelse(White >= 60 & Black < 20 & Hispanic < 20 & Asian < 20 & Native < 20 & HIPI < 20, "Predominantly White",
                       ifelse(Black >= 50 & White < 20 & Hispanic < 20 & Asian < 20 & Native < 20 & HIPI < 20, "Predominantly Black",
                        ifelse(Black < 20 & White < 20 & (Asian >= 50 | Hispanic >= 50 | Native >= 50 | HIPI >= 50), "Predominantly minoritized racial group other than Black", "Mixed"))))  %>%
  mutate(Composition = factor(Composition),
         bi_PW = ifelse(Composition == "Predominantly White", 1, 0),
         bi_PB = ifelse(Composition == "Predominantly Black", 1, 0),
         bi_PNB = ifelse(Composition == "Predominantly minoritized racial group other than Black", 1, 0),
         bi_mixed = ifelse(Composition == "Mixed", 1, 0)) %>%
  mutate(Pct_college = Pct_college / 100,
  Pct_Female = Pct_Female / 100,
  Pct_insurance = Pct_insurance / 100,
  Pct_Owner = Pct_Owner / 100, 
  Pct_Vacant = Pct_Vacant / 100,
  Pct_SingleFam = Pct_SingleFam /100,
  Urban_Rural_New = as.numeric(Urban_Rural_New))

df_composition$Composition <- relevel(df_composition$Composition, "Predominantly White")

df_composition <- df_composition %>%
  dplyr::filter(Urban_Rural_New == 1)
```

```{r}
table(df_composition$Composition)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Dilapidated Building 

df_prop_dilapbldg <- df_composition %>%
  dplyr::select(prop_dilapbldg, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam, State) %>%
  na.omit()

mod_na_fe1 <- lmer(prop_dilapbldg ~ Composition + (1|State),
                   data = df_prop_dilapbldg, REML=FALSE)

mod_na_cov_fe1 <- lmer(prop_dilapbldg ~ Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam + (1|State),
                       data = df_prop_dilapbldg, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Green Space

df_prop_green <- df_composition %>%
  dplyr::select(prop_green, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam , State) %>%
  na.omit()

mod_na_fe2 <- lmer(prop_green ~ Composition +(1| State),
                   data = df_prop_green, REML=FALSE)

mod_na_cov_fe2 <- lmer(prop_green ~ Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam +(1| State),
                       data = df_prop_green, REML=FALSE)
```


```{r, message=FALSE, warning=FALSE, include=FALSE}
### Crosswalk

df_prop_crosswalk <- df_composition %>%
  dplyr::select(prop_crosswalk, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam, State) %>%
  na.omit()

mod_na_fe3 <- lmer(prop_crosswalk ~ Composition + (1| State),
                   data = df_prop_crosswalk, REML=FALSE)

mod_na_cov_fe3 <- lmer(prop_crosswalk ~ Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam +(1| State),
                       data = df_prop_crosswalk, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Not single family home 

df_prop_not_single_family_home <- df_composition %>%
  dplyr::select(prop_not_single_family_home, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam, State) %>%
  na.omit()

mod_na_fe4 <- lmer(prop_not_single_family_home ~ Composition +(1| State),
                   data = df_prop_not_single_family_home, REML=FALSE)

mod_na_cov_fe4 <- lmer(prop_not_single_family_home ~ Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant +  Pct_SingleFam + (1| State),
                       data = df_prop_not_single_family_home, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Single Lane 

df_prop_single_lane <- df_composition %>%
  dplyr::select(prop_single_lane, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam, State) %>%
  na.omit()

mod_na_fe5 <- lmer(prop_single_lane ~ Composition +(1| State),
                   data = df_prop_single_lane, REML=FALSE)

mod_na_cov_fe5 <- lmer(prop_single_lane ~Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam +(1| State),
                       data = df_prop_single_lane, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# Table 2
tab_model(mod_na_cov_fe1, 
          mod_na_cov_fe2, 
          mod_na_cov_fe3, 
          mod_na_cov_fe4, 
          mod_na_cov_fe5, 
          show.se = FALSE,
          collapse.se = FALSE,
          col.order = c("est", "ci", "p"),
          show.stat = TRUE,
          show.ci = 0.95,
          collapse.ci = FALSE,
          p.style = "numeric",
          digits.p = 2,
          dv.labels = c("% Dilapidated", "% Green Space",  "% Crosswalk", "% Non-Single Family Home",  "% Single Lane", ""),
          pred.labels = c("Intercept",
                          "Mixed",
                          "Predominantly Black",
                          "Predominantly minoritized racial group other than Black",
                          "log(Household Income)",
                          "% College",
                          "Age",
                          "% Female",
                          "% Insured",
                          "% Owner",
                          "% Vacant",
                          "% Single Family"),
          CSS = list(
            modelcolumn1 = "background-color: #f0f0f0;", 
            modelcolumn3 = "background-color: #f0f0f0;", 
            modelcolumn5 = "background-color: #f0f0f0;"
  )
  ,
  file = "../Output/Table2.html"
)

### Null models (Supplementary Materials Table S2)
tab_model(mod_na_fe1, 
          mod_na_fe2, 
          mod_na_fe3, 
          mod_na_fe4, 
          mod_na_fe5, 
          show.se = FALSE,
          collapse.se = FALSE,
          col.order = c("response.level","est", "ci", "p"),
          show.stat = TRUE,
          show.ci = 0.95,
          collapse.ci = FALSE,
          p.style = "numeric",
          digits.p = 2,
          dv.labels = c("% Dilapidated", "% Green Space",  "% Crosswalk", "% Non-Single Family Home",  "% Single Lane", ""),
          pred.labels = c("Intercept",
                          "Mixed",
                          "Predominantly Black",
                          "Predominantly minoritized racial group other than Black"
                          
                          ),
          CSS = list(
            modelcolumn1 = "background-color: #f0f0f0;", 
            modelcolumn3 = "background-color: #f0f0f0;", 
            modelcolumn5 = "background-color: #f0f0f0;"
  )
  ,
  file = "../Output/TableS2.html"
)
```

### Supplementary Materials 

#### Section G Sensitivity Analysis 

##### Table S8. No cut-off

1. Predominantly white: Tracts where there are at least 60% of non-Hispanic whites
2. Predominantly black: Tracts that have at least 50% non-Hispanic blacks
3. Predominantly non-black minority: Tracts consist of at least 50% of a certain non-black minority 
Mixed: Tracts that cannot be classified into any of the typologies above. 

```{r, message=FALSE, warning=FALSE, include=FALSE}
df_composition <- df %>%
  dplyr::select(-geometry) %>%
  mutate(Composition = ifelse(White >= 60, "PW",
                       ifelse(Black >= 50, "PB",
                        ifelse(Asian >= 50 | Hispanic >= 50 | Native >= 50 | HIPI >= 50, "PNB", "Mixed"))))  %>%
  mutate(Composition = factor(Composition),
         bi_PW = ifelse(Composition == "PW", 1, 0),
         bi_PB = ifelse(Composition == "PB", 1, 0),
         bi_PNB = ifelse(Composition == "PNB", 1, 0),
         bi_mixed = ifelse(Composition == "Mixed", 1, 0)) %>%
  mutate(Pct_college = Pct_college / 100,
  Pct_Female = Pct_Female / 100,
  Pct_insurance = Pct_insurance / 100,
  Pct_Owner = Pct_Owner / 100, 
  Pct_Vacant = Pct_Vacant / 100,
  Pct_SingleFam = Pct_SingleFam /100,
  Urban_Rural_New = as.numeric(Urban_Rural_New))

df_composition$Composition <- relevel(df_composition$Composition, "PW")

df_composition <- df_composition %>%
  dplyr::filter(Urban_Rural_New == 1)
```

```{r}
table(df_composition$Composition)

```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Dilapidated Building 

df_prop_dilapbldg <- df_composition %>%
  dplyr::select(prop_dilapbldg, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam, State) %>%
  na.omit()

mod_na_fe1 <- lmer(prop_dilapbldg ~ Composition + (1|State),
                   data = df_prop_dilapbldg, REML=FALSE)

mod_na_cov_fe1 <- lmer(prop_dilapbldg ~ Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam + (1|State),
                       data = df_prop_dilapbldg, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Green Space

df_prop_green <- df_composition %>%
  dplyr::select(prop_green, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam , State) %>%
  na.omit()

mod_na_fe2 <- lmer(prop_green ~ Composition +(1| State),
                   data = df_prop_green, REML=FALSE)

mod_na_cov_fe2 <- lmer(prop_green ~ Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam +(1| State),
                       data = df_prop_green, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Crosswalk

df_prop_crosswalk <- df_composition %>%
  dplyr::select(prop_crosswalk, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam, State) %>%
  na.omit()

mod_na_fe3 <- lmer(prop_crosswalk ~ Composition + (1| State),
                   data = df_prop_crosswalk, REML=FALSE)

mod_na_cov_fe3 <- lmer(prop_crosswalk ~ Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam +(1| State),
                       data = df_prop_crosswalk, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Not single family home 

df_prop_not_single_family_home <- df_composition %>%
  dplyr::select(prop_not_single_family_home, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam, State) %>%
  na.omit()

mod_na_fe4 <- lmer(prop_not_single_family_home ~ Composition +(1| State),
                   data = df_prop_not_single_family_home, REML=FALSE)

mod_na_cov_fe4 <- lmer(prop_not_single_family_home ~ Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam +(1| State),
                       data = df_prop_not_single_family_home, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Single Lane 
df_prop_single_lane <- df_composition %>%
  dplyr::select(prop_single_lane, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam, State) %>%
  na.omit()

mod_na_fe5 <- lmer(prop_single_lane ~ Composition +(1| State),
                   data = df_prop_single_lane, REML=FALSE)

mod_na_cov_fe5 <- lmer(prop_single_lane ~Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam +(1| State),
                       data = df_prop_single_lane, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
### new table 
tab_model(mod_na_cov_fe1, 
          mod_na_cov_fe2, 
          mod_na_cov_fe3, 
          mod_na_cov_fe4, 
          mod_na_cov_fe5, 
          show.se = FALSE,
          collapse.se = FALSE,
          col.order = c("est", "ci", "p"),
          show.stat = TRUE,
          show.ci = 0.95,
          collapse.ci = FALSE,
          p.style = "numeric",
          digits.p = 2,
          dv.labels = c("% Dilapidated", "% Green Space",  "% Crosswalk", "% Non-Single Family Home",  "% Single Lane", ""),
          pred.labels = c("Intercept",
                          "Mixed",
                          "Predominantly Black",
                          "Predominantly minoritized racial group other than Black",
                          "log(Household Income)",
                          "% College",
                          "Age",
                          "% Female",
                          "% Insured",
                          "% Owner",
                          "% Vacant",
                          "% Single Family"),
          CSS = list(
            modelcolumn1 = "background-color: #f0f0f0;", 
            modelcolumn3 = "background-color: #f0f0f0;", 
            modelcolumn5 = "background-color: #f0f0f0;"
  )
  ,
  file = "../Output/Supplementary/TableS8.html"
)

### Null models
tab_model(mod_na_fe1, 
          mod_na_fe2, 
          mod_na_fe3, 
          mod_na_fe4, 
          mod_na_fe5, 
          show.se = FALSE,
          collapse.se = FALSE,
          col.order = c("response.level","est", "ci", "p"),
          show.stat = TRUE,
          show.ci = 0.95,
          collapse.ci = FALSE,
          p.style = "numeric",
          digits.p = 2,
          dv.labels = c("% Dilapidated", "% Green Space",  "% Crosswalk", "% Non-Single Family Home",  "% Single Lane", ""),
          pred.labels = c("Intercept",
                          "Mixed",
                          "Predominantly Black",
                          "Predominantly minoritized racial group other than Black"
                          
                          ),
          CSS = list(
            modelcolumn1 = "background-color: #f0f0f0;", 
            modelcolumn3 = "background-color: #f0f0f0;", 
            modelcolumn5 = "background-color: #f0f0f0;"
  )
  ,
  file = "../Output/Supplementary/TableS8 (null).html"
)
```

##### Table S9. 10% cut-off

1. Predominantly white: Tracts where there are at least 60% of non-Hispanic whites and no minority group represents more than 10%.
2. Predominantly black: Tracts that have at least 50% non-Hispanic blacks and no more than 10% of another racial/ethnic group
3. Predominantly non-black minority: Tracts consist of at least 50% of a certain non-black minority and no more than 10% of non-Hispanic blacks
Mixed: Tracts that annot be classified into any of the typologies above. 

```{r, message=FALSE, warning=FALSE, include=FALSE}
df_composition <- df %>%
  dplyr::select(-geometry) %>%
  mutate(Composition = ifelse(White >= 60 & Black < 10 & Hispanic < 10 & Asian < 10 & Native < 10 & HIPI < 10, "Predominantly White",
                       ifelse(Black >= 50 & White < 10 & Hispanic < 10 & Asian < 10 & Native < 10 & HIPI < 10, "Predominantly Black",
                        ifelse(Black < 10 & White < 10 & (Asian >= 50 | Hispanic >= 50 | Native >= 50 | HIPI >= 50), "Predominantly minoritized racial group other than Black", "Mixed"))))  %>%
  mutate(Composition = factor(Composition),
         bi_PW = ifelse(Composition == "Predominantly White", 1, 0),
         bi_PB = ifelse(Composition == "Predominantly Black", 1, 0),
         bi_PNB = ifelse(Composition == "Predominantly minoritized racial group other than Black", 1, 0),
         bi_mixed = ifelse(Composition == "Mixed", 1, 0)) %>%
  mutate(Pct_college = Pct_college / 100,
  Pct_Female = Pct_Female / 100,
  Pct_insurance = Pct_insurance / 100,
  Pct_Owner = Pct_Owner / 100, 
  Pct_Vacant = Pct_Vacant / 100,
  Pct_SingleFam = Pct_SingleFam /100,
  Urban_Rural_New = as.numeric(Urban_Rural_New))

df_composition$Composition <- relevel(df_composition$Composition, "Predominantly White")

df_composition <- df_composition %>%
  dplyr::filter(Urban_Rural_New == 1)
```

```{r}
table(df_composition$Composition)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Dilapidated Building 

df_prop_dilapbldg <- df_composition %>%
  dplyr::select(prop_dilapbldg, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam, State) %>%
  na.omit()

mod_na_fe1 <- lmer(prop_dilapbldg ~ Composition + (1|State),
                   data = df_prop_dilapbldg, REML=FALSE)

mod_na_cov_fe1 <- lmer(prop_dilapbldg ~ Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam + (1|State),
                       data = df_prop_dilapbldg, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Green Space

df_prop_green <- df_composition %>%
  dplyr::select(prop_green, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam , State) %>%
  na.omit()

mod_na_fe2 <- lmer(prop_green ~ Composition +(1| State),
                   data = df_prop_green, REML=FALSE)

mod_na_cov_fe2 <- lmer(prop_green ~ Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam +(1| State),
                       data = df_prop_green, REML=FALSE)
```


```{r, message=FALSE, warning=FALSE, include=FALSE}
### Crosswalk

df_prop_crosswalk <- df_composition %>%
  dplyr::select(prop_crosswalk, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam, State) %>%
  na.omit()

mod_na_fe3 <- lmer(prop_crosswalk ~ Composition + (1| State),
                   data = df_prop_crosswalk, REML=FALSE)

mod_na_cov_fe3 <- lmer(prop_crosswalk ~ Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam +(1| State),
                       data = df_prop_crosswalk, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Not single family home 

df_prop_not_single_family_home <- df_composition %>%
  dplyr::select(prop_not_single_family_home, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam, State) %>%
  na.omit()

mod_na_fe4 <- lmer(prop_not_single_family_home ~ Composition +(1| State),
                   data = df_prop_not_single_family_home, REML=FALSE)

mod_na_cov_fe4 <- lmer(prop_not_single_family_home ~ Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam + (1| State),
                       data = df_prop_not_single_family_home, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
### Single Lane 

df_prop_single_lane <- df_composition %>%
  dplyr::select(prop_single_lane, Composition, Median.household.income, Pct_college , Age, Pct_Female , Pct_insurance , Pct_Owner , Pct_Vacant , Pct_SingleFam, State) %>%
  na.omit()

mod_na_fe5 <- lmer(prop_single_lane ~ Composition +(1| State),
                   data = df_prop_single_lane, REML=FALSE)

mod_na_cov_fe5 <- lmer(prop_single_lane ~Composition + log(Median.household.income) + Pct_college + Age + Pct_Female + Pct_insurance + Pct_Owner + Pct_Vacant + Pct_SingleFam +(1| State),
                       data = df_prop_single_lane, REML=FALSE)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
### new table 
tab_model(mod_na_cov_fe1, 
          mod_na_cov_fe2, 
          mod_na_cov_fe3, 
          mod_na_cov_fe4, 
          mod_na_cov_fe5, 
          show.se = FALSE,
          collapse.se = FALSE,
          col.order = c("est", "ci", "p"),
          show.stat = TRUE,
          show.ci = 0.95,
          collapse.ci = FALSE,
          p.style = "numeric",
          digits.p = 2,
          dv.labels = c("% Dilapidated", "% Green Space",  "% Crosswalk", "% Non-Single Family Home",  "% Single Lane", ""),
          pred.labels = c("Intercept",
                          "Mixed",
                          "Predominantly Black",
                          "Predominantly minoritized racial group other than Black",
                          "log(Household Income)",
                          "% College",
                          "Age",
                          "% Female",
                          "% Insured",
                          "% Owner",
                          "% Vacant",
                          "% Single Family"),
          CSS = list(
            modelcolumn1 = "background-color: #f0f0f0;", 
            modelcolumn3 = "background-color: #f0f0f0;", 
            modelcolumn5 = "background-color: #f0f0f0;"
  )
  ,
  file = "../Output/Supplementary/TableS9.html"
)

### Null models
tab_model(mod_na_fe1, 
          mod_na_fe2, 
          mod_na_fe3, 
          mod_na_fe4, 
          mod_na_fe5, 
          show.se = FALSE,
          collapse.se = FALSE,
          col.order = c("response.level","est", "ci", "p"),
          show.stat = TRUE,
          show.ci = 0.95,
          collapse.ci = FALSE,
          p.style = "numeric",
          digits.p = 2,
          dv.labels = c("% Dilapidated", "% Green Space",  "% Crosswalk", "% Non-Single Family Home",  "% Single Lane", ""),
          pred.labels = c("Intercept",
                          "Mixed",
                          "Predominantly Black",
                          "Predominantly minoritized racial group other than Black"
                          
                          ),
          CSS = list(
            modelcolumn1 = "background-color: #f0f0f0;", 
            modelcolumn3 = "background-color: #f0f0f0;", 
            modelcolumn5 = "background-color: #f0f0f0;"
  )
  ,
  file = "../Output/Supplementary/TableS9 (null).html"
)
```

